### 2020-01-26 defesa/tex/chapter/definicoes.tex
wip

An ellipse is a curve which is categorized, along with the parabola and the hyperbola, as a conic section. 
They get this name because conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}. From that definition, an equation which describes any conic section is given as follows
\begin{equation}\label{equation:quadratic_form}
Ax^2 + Bxy + Cy^2 + Dx + Ey + F = 0,
\end{equation}
where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$. Distinguishing an ellipse from the other conic sections ca be done using the condition given by 
\begin{equation*}
4AC - B^2>0.
\end{equation*}
More details about conic sections can be found in \citeonline{ayoub}.

@@

Also, in \autoref{fig:ellipse_with_foci}, the distance $a = ||p_a - c||_2$, where $p_a$ is one of the intersection points of the ellipse with the major axis, is called the semi-major, and the distance $b = ||p_b-c||_2$, where $p_b$ is one of the intersection points of the ellipse with the minor axis, is called the semi-minor. These two values are also referred to as the shape parameters of an ellipse. Let $d = ||c-f_1||_2$, then it is easy to see that $a = R - d$ and $b = \sqrt{\frac{R^2}{4} - d^2}$.

Finally, an ellipse is said to be axis-parallel if its major-axis (see \autoref{fig:ellipse_with_foci}), which is the line that passes through its two foci points, is parallel to the $x$-axis.

@@

 \begin{align}\label{equation:pellipse}
 \begin{aligned}
 (p-c)^{T}Q(p-c) &= 1 & \Rightarrow \\
 (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) &= 1 & \Rightarrow\\
  \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} &= 1,&
   \end{aligned}
 \end{align}
where $a$ and $b$ are the semi-major and semi-minor shape parameters, respectively.

Also, the coverage region is determined by just changing the equality to an inequality as follows
\begin{equation}\label{equation:cover_pellipse}
\frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} \le 1.
\end{equation}

Another way to represent ellipses, which will be useful in some occasions, is through writing it as a curve function of the angle with its major-axis (see \autoref{fig:ellipse_params}).

@@

Let $c \in \R^2$ be the center of an ellipse with shape parameters $(a,b) \in \R^2_{>0}$. Then $\gamma\colon[0, 2\pi]\mapsto\R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
\begin{equation}\label{eq:parametric_ellipse}
\gamma(t) = \left\{
\begin{array}{l}
x(t)= a\cos{t} + c_x,\\
y(t)=b\sin{t} + c_y.
\end{array}
\right.
\end{equation}

Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$ centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$. Suppose that this line intersects the ellipse at least at one point. Plugging the line's equation into \autoref{equation:pellipse}, it is possible to obtain the distance between the intersection points. The final expression is given by
\begin{equation*}\label{eq:dist_line_ellipse}
D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
\end{equation*}
with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$. It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$. From that, we can conclude that if $m$ is fixed, the line that has the most distant intersection points with an ellipse is the one that passes through the origin; and also, that $D(m, c)$ attains every value in the range $[0, D(m, 0)]$. 
Following that, we define a function $L:m\mapsto\R_{>0}$ that describes the maximum squared distance between the points of the intersection of an ellipse with a line with a fixed angular coefficient:
\begin{equation}\label{eq:function-l}
L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2}.
\end{equation}
It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $x=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty\, 0]$, and attains every value in the interval $(4b^2, 4a^2]$. Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
In \autoref{fig:L-function-plot}, an example of function $L$ is shown with $(a, b) = (2, 1)$.

@@

A non-axis-parallel ellipse centered at $(c_x, c_y)\in\R^2$ can also be described by \autoref{def:ellipse}. Nonetheless, a simpler equation is going to be used here. Besides the center, and the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in \R$ is given. This new parameter represents the angle between the $x$-axis and the major-axis of the ellipse, this can be seen on \autoref{fig:rotated_ellipse}, where the dashed lines represent the ellipse's axes and the angle between the major-axis and the $x$-axis is displayed.

A rotated ellipse by $\theta$ can be transformed into a axis-parallel centered at the origin by applying two linear transformations: translation, so its center is at $(0, 0)$, then rotation so its major-axis is parallel to the $x$-axis. Reversing these transformations produces the following equation for a non-axis-parallel ellipse
\begin{equation}\label{eq:rotated_ellipse}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}=1.
\end{equation}
The coverage region of that same ellipse is given by every point $(x, y)\in\R^2$ that satisfies the following equation, which is the same as \autoref{eq:rotated_ellipse} with the equality sign $(=)$ replaced by $(\le)$
\begin{equation}\label{eq:rotated_ellipse_co}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}\le 1.
\end{equation}

Another important property of ellipses is shown on \autoref{fig:rotated_ellipse}. The two angles of rotation between the major-axis and the $x$-axis ($\theta$ and $\theta+\pi$) are actually equivalent -- they produce the same ellipse. This symmetry is true for any angle of rotation, which means that $\theta$ is equivalent to $\theta+k\pi$, $k\in\mathbb{Z}$. Therefore, it is possible to conclude that to represent any ellipse, it is enough to specify the domain of $\theta$ to be $[0, \pi)$.

@@

The set of complex numbers $\mathbb{C}$ is an extension of the set of real numbers $\R$ and can be very useful depending on the problem at hand. A thorough introduction on this topic is out of the scope and we just go through some basic properties that are going to be used later on \autoref{chapter:e3p}.

A complex number is composed of a real part added to an imaginary part which is a multiple of the imaginary unit $i = \sqrt{-1}$. This is expressed as $a + bi$, with $a, b \in \R$. Because $z$ is composed of two real numbers, the complex number system can be visualized on $\R^2$ as shown on \autoref{fig:complex-numbers}. This is also a good way to visualize Euler's Formula, as it can be also seen on \autoref{fig:complex-numbers}, which says that any complex number can be written in terms of its radius and polar angle as follows:
\begin{equation*}
z = re^{i\theta}=r(\cos{\theta} + i\sin{\theta}),
\end{equation*}
with $r$ being the length of the vector determined by the point $z$ on the complex plane and $\theta = angle(z)$ being its polar angle. Note that $angle$ is a function from $\mathbb{C}$ to $[0, 2\pi)$.
\begin{figure}[ht]
	\centering
	\def\svgwidth{\columnwidth}
	\includegraphics[scale=.37]{tex/figures/complex_numbers}
	\caption{The representation of a complex number on two dimensions.}
	\label{fig:complex-numbers}
\end{figure}

The complex conjugate is another important operator that is utilized later. Let $z = a + bi \in \mathbb{C}$, then we refer to $\bar{z}$ as the complex conjugate of $z$ and it is defined as:
\begin{equation*}
\bar{z} = a - bi.
\end{equation*}
Finally, we need to state two observations about the angles of $-z$ and $\bar{z}$ with respect to the angle of $z$, this will be useful later on \autoref{chapter:e3p}:
\begin{align*}
angle(\bar{z}) = 2\pi-angle(z),\\
angle(-z) = \pi + angle(z).
\end{align*}
Checking the validity of these two equalities can be done by just observing the symmetry between the points defined by $z, \bar{z},$ and $-z$ on the plane.

@@

 Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory. A very complete introduction to this algorithm can be found on \citeonline{watkins:2008}. The idea is to convert the input matrix to the Hessenberg form, after that, the matrix preserves its form through the iterations and, under some assumptions, convergence to the eigenvalues is achieved.
 Also, in \citeonline{barel} it is pointed that companion matrices are already in the Hessenberg form, making the Hessenberg conversion step unnecessary. This and other properties are used in \citeonline{barel} on the development of a $\bigO(n^2)$ algorithm for the specific case of companion matrices.

@@

The same definition found in \citeonline[p.~150]{powell} for real trigonometric polynomials is given here. They are also referred to as truncated Fourier Series in \citeonline{boyd:2006} and are given by
\begin{equation}\label{eq:trig_poly}
p_n(\theta) = \sum_{k=0}^{n} a_k\cos(k\theta) + \sum_{k=1}^{n} b_k\sin(k\theta).
\end{equation}
We say that $p_n: \R \mapsto \R$ as defined by \autoref{eq:trig_poly} is a $n$-degree real trigonometric polynomial. An important property is stated in \citeonline[p.~150]{powell}, which says that a $n$-degree polynomial can have up to $2n$ distinct roots on the interval $[0, 2\pi)$. It also says that a function written in the format
$$\begin{array}{cc}\cos^j{\theta}\sin^k{\theta}, & \quad j, k \in \mathbb{Z}_+, \end{array}$$
can be transformed into a real trigonometric polynomial of degree $j+k$. Therefore, the following expression also represents a $n$-degree real trigonometric polynomial
\begin{equation}\label{eq:trig_poly_2}
\sum_{0 \le j+k \le n}c_{j,k}\cos^j{\theta}\sin^k{\theta},
\end{equation}
for some $\{c_{j,k} \in \R: 0 \le j+k \le n\}$.

>>>>

An ellipse is a curve which is categorized, along with the parabola and the hyperbola, as a conic section. 
They get this name because conic sections are curves resulted from the intersection of a right circular cone in $\R^3$ with a plane \cite{brannan:geometry}. From that definition, an equation which describes any conic section is given as follows
\begin{equation}\label{equation:quadratic_form}
Ax^2 + Bxy + Cy^2 + Dx + Ey + F = 0,
\end{equation}
where $A,B,C,D,E,F \in \R$ are fixed and $x, y \in \R$. Distinguishing an ellipse from the other conic sections can be done using the condition
\begin{equation*}
4AC - B^2>0.
\end{equation*}
More details about conic sections can be found in \citeonline{ayoub}.

@@

Also, in \autoref{fig:ellipse_with_foci}, the distance $a = ||p_a - c||_2$, where $p_a$ is one of the intersection points of the ellipse with the major axis, is called the semi-major, and the distance $b = ||p_b-c||_2$, where $p_b$ is one of the intersection points of the ellipse with the minor axis, is called the semi-minor. These two values are also referred to as the shape parameters of an ellipse.
Finally, an ellipse is said to be axis-parallel if its major axis (see \autoref{fig:ellipse_with_foci}), which is the line that passes through its two foci points, is parallel to the $x$-axis.

@@

 \begin{align}\label{equation:pellipse}
 (p-c)^{T}Q(p-c) &= 1 & \Rightarrow \nonumber \\
 (\frac{p_x-c_x}{a^2}, \frac{p_y-c_y}{b^2})^{T}(p_x-c_x, p_y-c_y) &= 1 & \Rightarrow \nonumber\\
  \frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} &= 1,&
 \end{align}
where $(a, b) \in \R^2_{>0}$, with $a>b$, are ellipse's shape parameters.
Also, the coverage region is determined by just changing the equality to an inequality as follows
\begin{equation}\label{equation:cover_pellipse}
\frac{(p_x-c_x)^2}{a^2} + \frac{(p_y-c_y)^2}{b^2} \le 1.
\end{equation}

Another way to represent ellipses, which will be useful in some occasions, is through writing it as a curve function of the angle with its major axis (see \autoref{fig:ellipse_params}).

@@

Let $c \in \R^2$ be the center of an ellipse with shape parameters $(a,b) \in \R^2_{>0}$, with $a>b$. Then $\gamma\colon[0, 2\pi)\mapsto\R^2$ defines a curve which maps every angle onto a point on the ellipse and it is defined as follows
\begin{equation}\label{eq:parametric_ellipse}
\gamma(t) = \left\{
\begin{array}{l}
x(t)= a\cos{t} + c_x,\\
y(t)=b\sin{t} + c_y.
\end{array}
\right.
\end{equation}
Also, its derivative with respect to $t$ is given as follows
\begin{equation}\label{eq:der_parametric_ellipse}
\gamma'(t) = \left\{
\begin{array}{l}
x'(t)= -a\sin{t},\\
y'(t)=b\cos{t}.
\end{array}
\right.
\end{equation}

\subsection{The distance between points of an ellipse-line intersection}

Consider an ellipse with shape parameters $(a, b)\in\R^2_{>0}$, centered at the origin, and a line represented by the equation $y=mx+c$, with $m, c\in \R$. Suppose that this line intersects the ellipse at least at one point. Plugging the line's equation into \autoref{equation:pellipse}, it is possible to obtain the distance between the intersection points. The final expression is given by
\begin{equation*}\label{eq:dist_line_ellipse}
D(m, c)=\dfrac{\sqrt{(a^2m^2+b^2-c^2)(4a^2b^2(1+m^2))}}{(a^2m^2+b^2)},
\end{equation*}
with $D : \R^2 \mapsto \R_{\ge0}$ being a function of the line parameters $(m, c)$. It is also possible to see that, when $m$ is fixed, $D(m, c)^2$ is a parabola, and that $D(m, c)$ is maximized at $c=0$. From that, we can conclude that if $m$ is fixed, the line that has the most distant intersection points with an ellipse is the one that passes through the origin; and also, that $D(m, c)$ attains every value in the range $[0, D(m, 0)]$. 
Following that, we define a function $L:\R\mapsto\R_{>0}$ as

\begin{equation}\label{eq:function-l}
L(m):= D(m, 0)^2 = \dfrac{(a^2m^2+b^2)(4a^2b^2(1+m^2))}{(a^2m^2+b^2)^2},
\end{equation}
which describes the maximum distance between points of an ellipse-line intersection considering all lines with $m$ angular coefficient.

It is possible, by calculating the derivatives, to conclude that $L$ has its maximum at $m=0$, is increasing in $[0, \infty)$, is decreasing in $(-\infty\, 0]$, and attains every value in the interval $(4b^2, 4a^2]$. Notice that $L$ never hits $4b^2$ because that is the distance between the intersection of the ellipse with a vertical line.
In \autoref{fig:L-function-plot}, an example of function $L$ is shown with $(a, b) = (2, 1)$.

@@

A non-axis-parallel ellipse centered at $(c_x, c_y)\in\R^2$ can also be described by \autoref{def:ellipse}, nonetheless, in this work,  a simpler equation is used instead. 
Besides the center and the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$; an angle of rotation $\theta \in \R$ is given representing the angle between the $x$-axis and the major axis of the ellipse. This can be seen on \autoref{fig:rotated_ellipse}, where the dashed lines represent the ellipse's axes and the angle between the major-axis and the $x$-axis is displayed.

An ellipse rotated by $\theta$ can be transformed into an axis-parallel, and origin-centered ellipse by applying two linear transformations: translation to make its center be at $(0, 0)$, and rotation to make its major axis parallel to the $x$-axis. Reversing these transformations produces the following equation for a non-axis-parallel ellipse
\begin{equation}\label{eq:rotated_ellipse}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}=1.
\end{equation}
The coverage region of that same ellipse is given by every point $(x, y)\in\R^2$ that satisfies the following equation
\begin{equation}\label{eq:rotated_ellipse_co}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}\le 1,
\end{equation}
which is the same as \autoref{eq:rotated_ellipse} with the equality sign $(=)$ replaced by $(\le)$.

Another important property of ellipses is shown on \autoref{fig:rotated_ellipse}. The two angles of rotation between the major axis and the $x$-axis ($\theta$ and $\theta+\pi$) are equivalent -- they produce the same ellipse. This symmetry is true for any angle of rotation, which means that $\theta$ is equivalent to $\theta+k\pi$, $k\in\mathbb{Z}$. Therefore, to represent any ellipse, it is enough to specify the domain of $\theta$ as $[0, \pi)$.

@@

The set of complex numbers $\mathbb{C}$ can be seen as just an extension of the set of real numbers $\R$. A thorough introduction on this topic is out of the scope and we just go through some basic properties that are going to be used later in \autoref{chapter:e3p}.

Any complex number $z\in\mathbb{C}$ is composed of a real part $a\in\R$, and an imaginary part $b\in\R$, multiple of the imaginary unit $i = \sqrt{-1}$. This is expressed as $z=a+ib$. 
Because complex numbers are composed of two real numbers, mapping $\mathbb{C}$ to $\R^2$, as shown in  \autoref{fig:complex-numbers}, provides a good way to visualize the set of complex numbers. 
This is also a good way to visualize Euler's Formula. As it can be seen on \autoref{fig:complex-numbers}, any complex number can be written in terms of its radius and polar angle as

\begin{equation*}
z = re^{i\theta}=r(\cos{\theta} + i\sin{\theta}),
\end{equation*}
with $r$ being the length of the vector determined by the point $z$ on the complex plane and $\theta = angle(z)$ being its polar angle. Note that $angle$ is a function from $\mathbb{C}$ to $[0, 2\pi)$.
\begin{figure}[ht]
	\centering
	\def\svgwidth{\columnwidth}
	\includegraphics[scale=.37]{tex/figures/complex_numbers}
	\caption{The representation of a complex number on two dimensions.}
	\label{fig:complex-numbers}
\end{figure}

The complex conjugate is another important operator that is utilized later. Let $z = a + bi \in \mathbb{C}$, then we refer to $\bar{z}$ as the complex conjugate of $z$ and it is defined as
\begin{equation*}
\bar{z} = a - bi.
\end{equation*}
Lastly, two observations that are very important for the developments of \autoref{chapter:e3p} need to be stated. Let $z\in \mathbb{C}$, then we have 
\begin{align*}
angle(\bar{z}) = 2\pi-angle(z),\\
angle(-z) = \pi + angle(z).
\end{align*}
Checking the validity of these two equalities can be done by just observing the symmetry between the points defined by $z, \bar{z},$ and $-z$ on the plane.

@@

Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory (a very complete introduction to it can be found in \citeonline{watkins:2008}). 
The first step of the QR algorithm is to convert the input matrix into the Hessenberg form. This is done because matrices in the Hessenberg form maintain its form under the iterations of the algorithm. After that, the algorithm, under some assumptions, converges to the matrix's eigenvalues after $\bigO(n)$ iterations, each one taking $\bigO(n^2)$ computations.
Another method specific to companion matrices can be found in \citeonline{barel}. It uses the fact that companion matrices are already in the Hessenberg form to proposes a $\bigO(n^2)$ algorithm to find the roots of a $n$-degree polynomial.

@@

The same definition found in \citeonline[p.~150]{powell} for real trigonometric polynomials is given here. They are also referred to as truncated Fourier Series in \citeonline{boyd:2006} and are given by
\begin{equation}\label{eq:trig_poly}
p_n(\theta) = \sum_{k=0}^{n} a_k\cos(k\theta) + \sum_{k=1}^{n} b_k\sin(k\theta).
\end{equation}
We say that $p_n: \R \mapsto \R$ as defined by \autoref{eq:trig_poly} is a $n$-degree real trigonometric polynomial. An important property is stated in \citeonline[p.~150]{powell}, which says that a $n$-degree polynomial can have up to $2n$ distinct roots on the interval $[0, 2\pi)$. It also says that a function written in the format
$$\begin{array}{cc}\cos^j{\theta}\sin^k{\theta}, & \quad j, k \in \mathbb{Z}_+, \end{array}$$
can be transformed into a real trigonometric polynomial of degree $j+k$. Therefore, for some $\{c_{j,k} \in \R: 0 \le j+k \le n\}$, the expression
\begin{equation}\label{eq:trig_poly_2}
\sum_{0 \le j+k \le n}c_{j,k}\cos^j{\theta}\sin^k{\theta},
\end{equation}
also represents a $n$-degree real trigonometric polynomial.

### 2020-01-26 defesa/tex/chapter/mcd.tex
wip

In \citeonline{chazelle:1986} and \citeonline{cabello:2006}, on the other hand, instead of working directly with MCD1, an equivalent problem called \sigla{MWC}{Maximum Weight Clique} was introduced. The algorithm for MCD that is developed in this chapter also uses that equivalence. Because of that, MWC is introduced in the next section.

@@

In \autoref{fig:array_disks}, the intersection points between $\partial D_1$ (solid border) with $\partial D_2, \partial D_3$, and $\partial D_4$ (dashed border) are shown with a plus or minus sign indicating opening or closing intersection angles. 
The intersection list $B_1$ is also displayed in \autoref{fig:array_disks} along with the size of the set of active disks $Q$ after processing every point in $B_1$ -- this is exactly what \autoref{algoritmo:mcd_1} for MWC does for every disk. The region of optimal solutions is highlighted and can also be obtained by following $B_1$ while keeping track of $Q$.
The special intersection point of $\partial D_1$ with itself can also be seen in \autoref{fig:array_disks}. Its usage is very convenient as with $\Gamma_+(1, 1)$ and $\Gamma_-(1,1)$  in $B_1$, the algorithm inserts $D_1$ in the set of active disks before processing any point and removes $D_1$ only after every point has been processed.

@@

		\Procedure{CLS-MCD}{$\Pp, \Ww, r$}
		\State $S \gets \{\}$
		\ForAll{$p_i \in \Pp$}
		\State Let $D_i(p_i)$ be the disk with center at $p_i$
		\State Let $B_i$ be the list of intersection angles of $D_i$ as defined by \autoref{eq:b_i}

>>>>

The algorithm for MCD1, developed in this chapter, can be seen as a parallel version of the algorithm developed by \citeonline{drezner}.
We, however, based on \citeonline{chazelle:1986} and \citeonline{cabello:2006}, decided to work with an equivalent problem called \sigla{MWC}{Maximum Weight Clique} which is introduced in the next section.

@@

In \autoref{fig:array_disks}, the intersection points between $\partial D_1$ (solid border) with $\partial D_2, \partial D_3$, and $\partial D_4$ (dashed border) are shown with a plus or minus sign indicating opening or closing intersection angles. 
The intersection list $B_1$ is also displayed in \autoref{fig:array_disks} along with the size of the set of active disks $Q$ after processing a point in $B_1$ -- this is exactly what \autoref{algoritmo:mcd_1} for MWC does for every disk. 
It is possible to see that the optimal clique highlighted in \autoref{fig:array_disks} is enclosed by the arcs defined by $\Gamma_+(1,4)$ and $\Gamma_-(1,4)$, and can also be identified by following $B_1$ while keeping track of $Q$.
The special intersection point of $\partial D_1$ with itself can also be seen in \autoref{fig:array_disks}. Its usage is very convenient as with $\Gamma_+(1, 1)$ and $\Gamma_-(1,1)$  in $B_1$, the algorithm inserts $D_1$ in the set of active disks before processing any point, and removes $D_1$ only after every point has been processed.

@@

		\Procedure{CLS-MCD}{$\Pp, \Ww, r$}
		\State $S \gets \{\}$
		\ForAll{$p_i \in \Pp$}
		%\State Let $D_i(p_i)$ be the disk with center at $p_i$
		\State Let $B_i$ be the list of intersection angles of $\partial D_i(p_i)$ as defined by \autoref{eq:b_i}

### 2020-01-26 defesa/tex/chapter/mce.tex
wip

In this chapter, we introduce the version of PMCLP where every 
facility has an axis-parallel ellipse as its coverage area. We refer to this problem as \sigla{MCE}{Maximum Covering by Ellipses}. We also present an algorithm for it which is an adaptation of the algorithm developed for MCD in \autoref{chapter:pmclp}.

@@

\begin{align}
\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1 && (E_1) \label{eq:ell_inter_1}\\
\frac{(x-h)^2}{a^2} + \frac{(y-k)^2}{b^2} = 1 && (E_2), \nonumber
\end{align}
where $(h,k)\in\R^2$ is the center of the second ellipse after the coordinates were translated by $-q_1$. As both equations are equal to $1$, we have
\begin{align}
    b^2x^2 + a^2y^2 &= b^2(x-h)^2 + a^2(y-k)^2 \nonumber\\
    x &= y\frac{-2ka^2}{2hb^2} + \frac{b^2h^2 + a^2k^2}{2hb^2} \nonumber\\
    x &= y\alpha + \beta.\label{eq:ell_inter_2}
\end{align}
Replacing \autoref{eq:ell_inter_2} into \autoref{eq:ell_inter_1}, we get
\begin{align}\label{eq:ell_inter_3}
y^2(b^2\alpha^2 + a^2) + y(2\beta\alpha b^2) + b^2\beta^2 -a^2b^2 = 0,
\end{align}
Which is a second degree polynomial. Then, $\partial E_1(q_1) \cap \partial E_2(q_2) \neq \{\}$ if, and only if the roots of \autoref{eq:ell_inter_3} are real. The intersection points itself can be obtained by solving the polynomial for $y$ and applying its value onto the $x=y\alpha + \beta$ equation.

Suppose that $\partial E_1(q_1) \cap \partial E_2(q_2) = \{p_1, p_2\}$, with $p_1 \neq p_2$. To determine $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$, we need to first determine the angles of intersection of $p_1$ and $p_2$ on $E_1(q_1)$ using the parametric equation for an ellipse defined in \autoref{eq:parametric_ellipse}. Given a point $(x, y)\in \partial E_1(q_1)$, using \autoref{eq:parametric_ellipse} we have

\begin{equation*}
\dfrac{a}{b}\dfrac{y-q_{1y}}{x-q_{1x}} = \tan{t}.
\end{equation*}
Solving for $t$ gives the angle of point $(x,y)$ on $E_1(q_1)$. Using that process we obtain $t^{(1)}_1, t^{(1)}_2$ as the angles of the points $\{p_1, p_2\}$ on $E_1(q_1)$; and $t^{(2)}_1, t^{(2)}_2$ as the angles of points $\{p_1, p_2\}$ on $E_2(q_2)$.
Let $\gamma_1$ be the curve defined by $E_1(q_1)$ and $\gamma_2$ the curve defined by $E_2(q_2)$. Considering its derivatives \autoref{eq:der_parametric_ellipse} at the intersection points, as it can be seen in \autoref{fig:ellipse_gamma}, we have that $p_1$ is $\Gamma_+(1,2)$ if, and only if
\begin{equation*}
angle(\gamma_1'(t_1^{(1)}), -\gamma_2'(t_1^{(2)}) < \pi.
\end{equation*}
The case where that angle is equal to $\pi$ happens when both ellipses intersect at only one point. This case has to be treated separately as we need to have two equal intersection points: one as $\Gamma_+(1,2)$ and the other as $\Gamma_-(1,2)$.

@@

	\caption{The intersection list of a disk with three other disks.}
	%\input{tex/figures/array_disks.tex}
	\includegraphics[scale=.38]{tex/figures/ellipse_gamma.pdf}
	\fautor
	\label{fig:ellipse_gamma}
\end{figure}

@@

Finally, \autoref{algoritmo:mce} can serve as basis for the \autoref{algoritmo:mce-k} for MCE-$k$. 
Firstly, for every subset $I \subset \{1, \dots, m\}$, such that $|I| = k$, the algorithm for MCE is invoked for the instance $(\Pp, \Ww, \{(a_j, b_j) : j \in I\})$; that is, an instance where only the ellipses in $I$ are present.
After that, by keeping track of the utilized ellipses' costs for every $I \subset \{1, \dots, m\}$, an optimal solution can be obtained.
This simple adjustment achieves a run-time complexity of $\bigO(\binom{m}{k} \times n^{2k}) = \bigO(n^{3m})$.

@@

        \If{$w(Cov) + w(\cup_{k=j+1}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
        \State $(q_j^*, \dots, q_j^*) \gets(q_j, \dots, q_m)$
        \EndIf
        \EndFor

>>>>

In this chapter, we introduce the version of PMCLP where every 
facility has an axis-parallel ellipse as its coverage area. We refer to this problem as \sigla{MCE}{Maximum Covering by Ellipses}. We also present an algorithm for it which is an adaptation of the one developed for MCD in \autoref{chapter:pmclp}.

@@

\begin{align}
\frac{x^2}{a^2} + \frac{y^2}{b^2} = 1 && (E_1) \label{eq:ell_inter_1}\\
\frac{(x-h)^2}{a^2} + \frac{(y-k)^2}{b^2} = 1 && (E_2), \nonumber
\end{align}
where $(h,k)\in\R^2$ is the center of the second ellipse after the coordinates were translated by $-q_1$. As both equations are equal to $1$, we have
\begin{align}
    b^2x^2 + a^2y^2 &= b^2(x-h)^2 + a^2(y-k)^2 \nonumber\\
    x &= y\frac{-2ka^2}{2hb^2} + \frac{b^2h^2 + a^2k^2}{2hb^2} \nonumber\\
    x &= y\alpha + \beta.\label{eq:ell_inter_2}
\end{align}
Replacing \autoref{eq:ell_inter_2} into \autoref{eq:ell_inter_1}, we get
\begin{align}\label{eq:ell_inter_3}
y^2(b^2\alpha^2 + a^2) + y(2\beta\alpha b^2) + b^2\beta^2 -a^2b^2 = 0,
\end{align}
which is a second degree polynomial. Then, $\partial E_1(q_1) \cap \partial E_2(q_2) \neq \{\}$ if, and only if the roots of \autoref{eq:ell_inter_3} are real. The intersection points itself can be obtained by solving the polynomial for $y$ and plugging its value back into the $x=y\alpha + \beta$ equation.

Suppose that $\partial E_1(q_1) \cap \partial E_2(q_2) = \{p_1, p_2\}$, with $p_1 \neq p_2$. To determine $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$, we need to first determine the intersection angles corresponding to $p_1$ and $p_2$ on $E_1(q_1)$.

Let $\gamma_1$ and $\gamma_2$ be two curves defined as \autoref{eq:parametric_ellipse} for $E_1(q_1)$ and $E_2(q_2)$ respectively. 
The intersection angle of $p_i$ in $E_j(q_j)$ is defined as $t_i^{(j)} \in [0, 2\pi)$, such that $\gamma_j(t_i^{(j)}) = p_i$, for $i, j \in \{1, 2\}$. Obtaining $t_i^{(j)}$ can be done analytically solving the equation

\begin{equation*}
	\dfrac{a}{b}\dfrac{p_{iy}-q_{jy}}{p_{ix}-q_{jx}} = \tan{(t_i^{(j)})}.
\end{equation*}

Let $\gamma_1'$ and $\gamma_2'$ be the derivatives of $\gamma_1$ and $\gamma_2$ respectively as defined by \autoref{eq:der_parametric_ellipse}. Then, considering the tangent vectors $\gamma_1'(t_i^{(1)})$ and $-\gamma_2'(t_i^{(2)})$, $i\in \{1, 2\}$, as shown in \autoref{fig:ellipse_gamma}, we can define a function $\phi_{1,2}\colon \{p_1, p_2\} \to \{\Gamma_+(1,2), \Gamma_-(1,2)\}$ that takes an intersection point and returns its corresponding closing/opening intersection angle as

\begin{equation*}
\phi_{1,2}(p_i) = \begin{cases}
\Gamma_+(1,2) & angle(\gamma_1'(t_i^{(1)}), -\gamma_2(t_i^{(2)})) > \pi\\
\Gamma_-(1,2) & angle(\gamma_1'(t_i^{(1)}), -\gamma_2(t_i^{(2)})) < \pi.
\end{cases}
\end{equation*}
At last, the case where that angle is equal to $\pi$ happens only when both ellipses intersect at only one point. This case has to be treated separately as, by \autoref{def:inter_arc}, we need to have two equal intersection points: one as $\Gamma_+(1,2)$ and the other as $\Gamma_-(1,2)$.

@@

	\caption{Determining $\Gamma_+(1,2)$ and $\Gamma_-(1,2)$.}
	%\input{tex/figures/array_disks.tex}
	\includegraphics[scale=.38]{tex/figures/ellipse_gamma.pdf}
	\fautor
	\label{fig:ellipse_gamma}
\end{figure}

@@

Finally, \autoref{algoritmo:mce} can serve as basis for MCE-$k$'s \autoref{algoritmo:mce-k}. 
Firstly, for every subset $I \subset \{1, \dots, m\}$, such that $|I| = k$, the algorithm for MCE is invoked for the instance $(\Pp, \Ww, \{(a_j, b_j) : j \in I\})$; that is, an instance where only the ellipses in $I$ are present.
After that, by keeping track of the utilized ellipses' costs for every $I \subset \{1, \dots, m\}$, an optimal solution can be obtained.
This simple adjustment achieves a run-time complexity of $\bigO(\binom{m}{k} \times n^{2k}) = \bigO(n^{3m})$.

@@

        \If{$w(\cup_{k=j}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
        \State $(q_j^*, \dots, q_j^*) \gets(q_j, \dots, q_m)$
        \EndIf
        \EndFor
